A community-maintained standard library of population genetic simulations

### 2019-12-18 popSimManu.tex

\stdpopsim allows us to readily compare these estimates to those drawn from a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but a different demographic
history -- that inferred by \cite{gutenkunst2009inferring}. Again we see that each
of the methods is capturing relevant parts of the population history, although the
degree of noise at any given time interval varies. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated samples are generally better across methods than estimates from the YRI simulations.

@@

In Figure \ref{fig:IM_popn_human}C we show estimates of population sizes and divergence
time from each of the methods for samples simulated for the African and European populations
under the \cite{gutenkunst2009inferring} model. Each of the methods compared has stronger
and weaker points to their accuracy across parameters. For instance the simple, IM-style
analyses we have performed do not capture recent population size change in CEU, however
they do a good job of estimating the more simple simulated YRI population size history.

@@

The broad brush comparisons we have done, while far from exhaustive, are informative,
and highlight the utility of easy comparison of methods on the same footing.
The tests here were under best-case scenarios --
simulations of discrete, randomly mating populations that evolve neutrally and 
fit the assumptions of the methods nearly exactly --
and yet different methods, as well as applications of the same method
to different simulations of the same model,
produced somewhat different results.

>>>>

\stdpopsim allows us to readily compare these estimates to those drawn from a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but a different demographic
history -- that inferred by \cite{gutenkunst2009inferring}. Again we see that each
of the methods is capturing relevant parts of the population history, although the
discrepancy between inferred and simulated values is changes over time. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated populations are generally better across methods than estimates from the YRI
simulated population.

@@

In Figure \ref{fig:IM_popn_human}C we show estimates of population sizes and divergence
time from each of the methods for samples simulated for the African and European populations
under the \cite{gutenkunst2009inferring} model. Each of the methods compared has stronger
and weaker points to their accuracy across parameters. For instance the simple, IM-style
analyses we have performed do not capture recent population size change in CEU, however
they do a good job of estimating the simpler simulated YRI population size history.

@@

The broad brush comparisons we have done, while far from exhaustive, are informative,
and highlight the utility of easy comparison of methods on the same footing.
The tests here were under best-case scenarios --
simulations of discrete, randomly mating populations that fit the assumptions of the methods nearly exactly --
and yet different methods, as well as applications of the same method
to different simulations of the same model,
produced somewhat different results.
